\documentclass[12pt]{article}
\usepackage{amsfonts,amsmath}

\begin{document}

\section{Introduction}

% Begin Excerpt
This applet was written to accompany the article \textit{They Say That Breaking Up is Hard to Do: Decomposing Compositions.}  The applet investigates the properties of finite Blaschke products, functions $B$ defined by $$B(z) = \lambda\prod_{j = 1}^n \frac{z - a_j}{1 - \overline{a_j}z}, ~\mbox{where}~ |a_j| < 1~\mbox{and}~|\lambda| = 1.$$ This class of functions is precisely the set of functions analytic on the open unit disk $\mathbb{D}$, continuous on its closure, mapping $\mathbb{D}$ to itself and the unit circle, $\mathbb{T}$ to itself.  The article is concerned with determining when a Blaschke product is a composition, and it provides three algorithms for doing so. The first applet is straightforward computation, while the second and third algorithms can be carried out using this applet.
% End Excerpt

The applet requires a modern HTML5 web browser (Chrome, Safari, or Firefox are recommended for best performance).

\section{Using the Applet}

On the applet, the small white circles indicate the zeroes ${a_j}$ of a Blaschke product $B$, and the gray circles are the ``critical points,'' points $z$ where $B'(z) = 0$.  The applet also displays a table of coordinates for the critical points as well as a table for $B$'s ``critical values'' (the images of the critical points).

One can move the zeroes of the Blaschke product by dragging the white circles, add zeroes by double-clicking on the graph, and remove a zero by dragging it outside of the circle.  (It is assumed that $B(0) = 0$, so the zero at zero cannot be changed.)  Hovering the mouse cursor over a critical point in the table will highlight it on the graph, and doing the same to a critical value will highlight every critical point that maps to that value.  Clicking on the plot will display the coordinates of the click under ``Click Location'' as well as the value of $B$ at that point.

Once the zeroes have been configured, clicking the ``Plot'' button will generate a color plot of $arg(B)$ over the disk.  If the zeroes are modified, clicking ``Plot'' again will regenerate the graph.

The applet also generates a pair of plots each of which divide the disk into regions.  The plot labeled ``Region Images'' divides the disk into sectors whose edges are the arguments of the critical values (which are displayed on the plot as grey dots).  The ``Region Preimages'' plot shows the preimages of those sectors.  Clicking in the ``Images'' plot and moving the mouse will draw preimages of those points in the ``Preimages'' plot.  This allows you to trace out a path and see the several paths in the domain which map to it.  The ``Clear Preimages'' button will erase these points.
%Observe that on the left plot, each region is adjacent to exactly one zero, and each zero is adjacent to a region of each color.  This shows that a Blaschke product with $n$ zeroes maps the disk to itself $n$ times, since putting all the regions together makes a complete copy of the disk.

Given a point $\omega$ on the unit circle $\mathbb{T}$ and a Blaschke product $B$ with $n$ zeroes, there will be $n$ points (each also on the unit circle) such that $B(z) = \omega.$  The applet can draw connecting lines between these preimages.  In the ``Preimages'' plot, clicking on a point $e^{i\theta}$ on the unit circle will connect all points $z$ where $B(z)=B(e^{i\theta})$ in order of increasing argument.  Entering a value $N$ in the ``Skip Points'' box will instead connect every $N$th point.  Clicking ``Redraw Lines'' will automatically identify several points on the unit circle(the number of such points is controlled by the ``Auto Identify Points'' parameter.)  Finally, checking ``Auto Re-Draw'' will automatically draw lines as the zeroes of the Blaschke product are manipulated.  The curves generated by these lines are used in (reference to section 5 of the paper.)

\end{document}
